---
title: "Case Study"
author: "My An Huynh"
date: "2024-10-09"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load necessary packages 
```{r}
library(p8105.datasets)
library(leaflet)
data(nyc_airbnb)
```

## Brainstorm questions

*What are max and min prices
  *what are average prices?
  *what factors affect prices? how much does location or room type matter?
*Where are prices going up and down over time?
*What's the relatinship between number of reviews and average review
*Does room type affect availability?
*What's the location of the unit?
  *What areas are popular?
  *Does popularity equal number of units? Average prices?
*Are there repeat hosts?
  *If so, what does that mean?
  
```{r}
nyc_airbnb |> 
  group_by(neighbourhood, neighbourhood_group) |> 
  summarize(
    location_number = n(),
    .group = "drop"
  ) |> 
  mutate(
    rank_neighborhood = min_rank(desc(neighbourhood_group))
  )
```

```{r}
nyc_airbnb |> 
  group_by(neighbourhood_group, room_type) |> 
  summarize(
    median_price = median(price)
  ) |> 
  pivot_wider(
    names_from = room_type, 
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point()
```


```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price <1000) |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.1)

```

```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price <1000,
    room_type == "Entire home/apt"
      ) |> 
  group_by(neighbourhood) |> 
  summarize(mean_price = mean(price)) |> 
  arrange(desc(mean_price)) 
  
```


```{r}
nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price <1000,
    room_type == "Entire home/apt"
      ) |> 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, price)
  ) |> 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  
```

Go back to that map 

```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location
  )

nyc_airbnb |> 
  filter(
    neighbourhood_group == "Manhattan",
    price <1000) |> 
  slice(1:10) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.positron) |> 
  addCircleMarkers(~lat, ~long, color = ~ pal(review_scores_location), radius = 2)

```

